Reactor like TGE model

### 2019-04-13 AYSS-2019/presentation/main.tex
ayss 2019

\begin{document}
    % титульный слайд
    \begin{frame}
        \titlepage
    \end{frame}
\begin{frame}
   \frametitle{}

@@

\begin{frame}
\frametitle{}

\begin{frame}
\frametitle{History}

@@

\end{frame}
\usebackgroundtemplate{}
\begin{frame}
\frametitle{Reactor Like TGE model}

@@

\begin{frame}
    \frametitle{}
\begin{columns}
	\begin{column}{0.5\textwidth}
		\begin{figure}[htb]
		\centering
		\includegraphics[width=1\columnwidth]{proofTGF.pdf}
		\end{figure}
		The first figure shows the case of an explosive growth in the number of secondary photons that are well suited to the phenomenon of TGF.
	\end{column}
	\begin{column}{0.5\textwidth}
		\begin{figure}[htb]
			\centering
			\includegraphics[width=1\columnwidth]{Extinction.pdf}
		\end{figure}
		The second figure demonstrates the case when there was a dissipation of an avalanche that had just begun to develop.

@@

\begin{frame}
    \frametitle{}

@@

    		\begin{figure}[htb]
    			\centering
    			\includegraphics[width=1\columnwidth]{proofTGE.pdf}
    		\end{figure}
    		The third figure demonstrates the case of a slower and less intensive growth. Such processes with some minor adjustments and assumptions about field dynamics could describe TGE phenomenon.	
    	\end{column}
    \end{columns}

>>>>

\begin{document}
    % титульный слайд
    \begin{frame}
        \titlepage
    \end{frame}
%\begin{frame}
%   \frametitle{}
% 
%\end{frame}
%
\begin{frame}
\frametitle{Thunderstorm cloud and lighting: paths for research}

@@

\begin{frame}
\frametitle{History}
	\begin{columns}
		\begin{column}{0.5\textwidth}
			TGF ---
		\end{column}
		\begin{column}{0.5\textwidth}
			TGE ---
		\end{column}
	\end{columns}
\end{frame}

@@

\end{frame}
\usebackgroundtemplate{}
%\begin{frame}
%\frametitle{Reactor Like TGE model}
%
%\end{frame}

@@

\begin{frame}
    \frametitle{Results}
\begin{columns}
	\begin{column}{0.5\textwidth}
		\begin{figure}[htb]
		\centering
		\includegraphics[width=1\columnwidth]{proofTGF.pdf}
		\end{figure}
		This figure shows the case of an \textbf{explosive growth} in the number of secondary photons that are well suited to the phenomenon of \textbf{TGF}.
	\end{column}
	\begin{column}{0.5\textwidth}
		\begin{figure}[htb]
			\centering
			\includegraphics[width=1\columnwidth]{Extinction.pdf}
		\end{figure}
		This figure demonstrates the case when there was a \textbf{dissipation of an avalanche} that had just begun to develop.

@@

\begin{frame}
    \frametitle{Results}

@@

    		\begin{figure}[htb]
    			\centering
    			\includegraphics[width=1\columnwidth]{proofTGE.pdf}
    		\end{figure}
    		This figure demonstrates the case of a \textbf{slower and less intensive growth}. Such processes with some minor adjustments and assumptions about field dynamics could describe \textbf{TGE} phenomenon.	
    	\end{column}
    \end{columns}
